---
title: "Usage-FreeHiC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage-FreeHiC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

FreeHi-C (v2.0) is short for Fragment interactions empirical estimation for fast simulation of Hi-C data. It is a data-driven Hi-C data simulator for simulating and augmenting Hi-C datasets. FreeHi-C employs a non-parametric strategy for estimating an interaction distribution of genome fragments and simulates Hi-C reads from interacting fragments. Data from FreeHi-C exhibit higher fidelity to the biological Hi-C data. FreeHi-C not only can be used to study and benchmark a wide range of Hi-C analysis methods but also boosts power and enables false discovery rate control for differential interaction detection algorithms through data augmentation. Different from FreeHi-C (v1.0), a spike-in module is added enabling the simulation of true differential chromatin interactions.

## Usage

```{r setup}
library(FreeHiCLite)
```

### FreeHi-C

### SpikeIn

## References

